03_wrangle

### 2020-05-13 analysis/03_datawrangling.Rmd
rename
now with WGCNA as step 5, wrangle as 6

---
title: "03_DESeq2part2"
output: md_document
---

@@

# genes from Ch 17 Evolution of parental care
curleychampagnegenes <- c("AVP", "AVPR1A", "ADRA2A",    
                          "COMT", "CRH", "CRHBP", "CRHR1", "CRHR2", 
                          "DRD1", "DRD4","ESR1", "ESR2", #ERa ERbeta
                          "FOS", "HTR2C", "MEST", "NR3C1", #GR
                          "OPRM1", "OXT" , "PGR", "PRL", "PRLR",  "SLC6A4") #5HTT
curleychampagnegenes
curleychampagnegenes <- as.data.frame(curleychampagnegenes) %>%
  mutate(GO = "parentalcare", gene = curleychampagnegenes)  %>%
  select(GO, gene)

@@

parentalcaregenes <- GOgenesLong %>% 
  pivot_wider(
    names_from = GO,
    values_from = gene) %>%
  mutate(numGOs = 4 - rowSums(is.na(.))) %>%
  arrange(desc(numGOs)) %>%
  select(-numGOs) %>%
  left_join(geneids, by = c("geneid","NCBI"))
head(parentalcaregenes)

candidategenes <- parentalcaregenes %>% distinct(gene) %>% pull(gene)

# note: I can't find these genes in dataset: NOS1 or OXTR or FOX1B or HTR5A

@@

```{r write}
write.csv(allDEG, "../results/03_allDEGs.csv")
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
```

>>>>

---
title: "03_wrangle"
output: md_document
---

@@

# genes from Ch 17 Evolution of parental care
curleychampagnegenes <- c("AVP", "AVPR1A", "ADRA2A",    
                          "COMT", "CRH", "CRHBP", "CRHR1", "CRHR2", 
                          "DRD1", "DRD4","ESR1", "ESR2", #ERa ERbeta
                          "FOS", "HTR2C", "MEST", "NR3C1", #GR
                          "OPRM1", "OXT" , "PGR", "PRL", "PRLR",  "SLC6A4") #5HTT
curleychampagnegenes
curleychampagnegenes <- as.data.frame(curleychampagnegenes) %>%
  mutate(GO = "literature", gene = curleychampagnegenes)  %>%
  select(GO, gene)

@@

parentalcaregenes <- GOgenesLong %>% 
  pivot_wider(
    names_from = GO,
    values_from = gene,
    values_fill = list(gene = "")) %>%
  left_join(geneids, by = c("geneid","NCBI")) %>%
  dplyr::rename("GO"= "parentalbehavior" )
head(parentalcaregenes)

candidategenes <- parentalcaregenes %>% distinct(gene) %>% pull(gene)
# note: I can't find these genes in dataset: NOS1 or OXTR or FOX1B or HTR5A
```

@@

```{r write}
write.csv(allDEG, "../results/03_allDEGs.csv")
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(parentalcaregenes, "../metadata/03_parentalcaregenes.csv")
```
